---
title: "2013-2019 Homeless Children Map"
author: "Seiter"
date: "4/28/2020"
output: html_document
---
 
```{r}
library("rio")
library("janitor")
library("tidyverse")
library("lubridate")
```
Load 2013-2014 Data
```{r include=FALSE}
AR2013_14 <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/2013-2014-demographics-data-for-districts-2.xlsx?raw=true", which = "Data", skip=8)
```
Clean up column names so they are R friendly
```{r}
AR2013_14 <- janitor::clean_names(AR2013_14)
```
Create 2013-2014 table with only relevant columns
```{r}
table2013 <- AR2013_14 %>%
  select(district_name, district_percent_homeless, district_lea) %>%
  arrange(desc(district_percent_homeless))
```
Rename column
```{r}
colnames(table2013)[2] <- "Pct_Homeless_2013"
```
Load 2018-2019 Data
```{r}
AR2018_19 <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/Homeless_Children/2018-2019-demographic-data-for-districts.xlsx?raw=true", which = "Data", skip=8)
```
Clean 2018-2019 column names
```{r}
AR2018_19 <- janitor::clean_names(AR2018_19)
```
Create 2018-2019 table
```{r}
table2018 <- AR2018_19 %>%
  select(district_name, district_percent_homeless, district_lea) %>%
  arrange(desc(district_percent_homeless))
```
Rename column
```{r}
colnames(table2018)[2] <- "Pct_Homeless_2018"
```
Join tables
```{r}
AR2013_19 <- table2018 %>% 
  inner_join(table2013, by=("district_lea"))
```
Use anti_join to determine the lost records
```{r}
leftout <- table2013 %>% 
  anti_join(table2018, by=("district_lea"))
```
Load Data
```{r}
School_Address <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/SDI%20Districts%20Printed-02-26-2020-11_38_05.xlsx?raw=true", skip =1)
```
Convert School address LEA to numeric and match
```{r}
School_Address$LEA <- as.numeric(School_Address$LEA)
colnames(AR2013_19)[3] <- "LEA"
AR2013_19$LEA <- as.numeric(AR2013_19$LEA)
```
Now we join School_Address to table2009_19
```{r}
abc <- School_Address %>% 
  select(LEA, Name, Address) %>% 
  inner_join(AR2013_19, by="LEA")
```
Use anti_join to determine the lost records
```{r}
leftout2 <- School_Address %>% 
  select(LEA, Name, Address) %>% 
  anti_join(AR2013_19, by="LEA")
```

Form new table
```{r}
Addresses <- abc %>%
  select(LEA, district_name.x, Address, Pct_Homeless_2018, Pct_Homeless_2013)
glimpse(Addresses)
```

Rename columns
```{r}
colnames(Addresses)[2] <- "district_name"
```

Calculate percent change in homelessness from 2013 to 2019
```{r}
ARaddresses <- Addresses %>% 
  mutate(PctChg = (Pct_Homeless_2018-Pct_Homeless_2013)/Pct_Homeless_2013) 
colnames(ARaddresses)[6] <- "Pct_Chg"
glimpse(ARaddresses)
```
write.csv(ARaddresses, "2013ARaddresses.csv")

