---
title: "Homeless Children Map April 21, 2020"
author: "Katy Seiter"
date: "4/21/2020"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 4
---
 
## Reporting on Homelessness: Data Analysis for Journalists   

#### Jour 405v, Jour 5003, Spring 2020    

--------------------------------------------------------------------
# Part 1: Homeless Children Data
Load tidyverse, janitor, lubidate
```{r include=FALSE}

library(rio)
library(tidyverse)
library(janitor)
library(lubridate)
```
Load 2009-2010 Data
```{r include=FALSE}
AR2009_10 <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/Homeless_Children/2009-2010-demographics-data-for-districts.xlsx?raw=true", which = "Data", skip=8)
```
Clean up column names so they are R friendly
```{r}
AR2009_10 <- janitor::clean_names(AR2009_10)
```
Create 2009-2010 table with only relevant columns
```{r}
table2009 <- AR2009_10 %>%
  select(district_name, district_percent_homeless, district_lea) %>%
  arrange(desc(district_percent_homeless))
```
Rename column
```{r}
colnames(table2009)[2] <- "Pct_Homeless_2009"
```
Load 2018-2019 Data
```{r}
AR2018_19 <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/Homeless_Children/2018-2019-demographic-data-for-districts.xlsx?raw=true", which = "Data", skip=8)
```
Clean 2018-2019 column names
```{r}
AR2018_19 <- janitor::clean_names(AR2018_19)
```
Create 2018-2019 table
```{r}
table2018 <- AR2018_19 %>%
  select(district_name, district_percent_homeless, district_lea) %>%
  arrange(desc(district_percent_homeless))
```
Rename column
```{r}
colnames(table2018)[2] <- "Pct_Homeless_2018"
```
Join tables
```{r}
AR2009_19 <- table2018 %>% 
  inner_join(table2009, by=("district_lea"))
```
Use anti_join to determine the lost records
```{r}
leftout <- table2009 %>% 
  anti_join(table2018, by=("district_lea"))
```
Load Data
```{r}
School_Address <- rio::import("https://github.com/profrobwells/HomelessSP2020/blob/master/Data/SDI%20Districts%20Printed-02-26-2020-11_38_05.xlsx?raw=true", skip =1)
```
Convert School address LEA to numeric and match
```{r}
School_Address$LEA <- as.numeric(School_Address$LEA)
colnames(AR2009_19)[3] <- "LEA"
AR2009_19$LEA <- as.numeric(AR2009_19$LEA)
```
Now we join School_Address to table2009_19
```{r}
abc <- School_Address %>% 
  select(LEA, Name, Address) %>% 
  inner_join(AR2009_19, by="LEA")
```
Form new table
```{r}
Addresses <- abc %>%
  select(LEA, district_name.x, Address, Pct_Homeless_2018, Pct_Homeless_2009)
glimpse(Addresses)
```

Rename columns
```{r}
colnames(Addresses)[2] <- "district_name"
```

```{r}
ARaddresses <- Addresses %>% 
  mutate(difference = Pct_Homeless_2018-Pct_Homeless_2009)
glimpse(ARaddresses)
colnames(ARaddresses)[6] <- "Pct_Chg"
```

write.csv(ARaddresses, "ARaddresses.csv")